Run the model

### 2019-06-24 scripts/model/2_run_model.Rmd
Ready for submission as a Report

@@

params %>% 
  knitr::kable(col.names = c("Parameter", "Value", "Source"),
               format = "latex",
               escape = F) %>% 
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  cat(file = here("docs", "tab", "parameters.tex"))
```

@@

shorter_trading <- DF_1_with_trading %>% 
  select(Country, R, theta, Vessel_Days_trading = Vessel_Days, pi_trading = VDSprice, VDSrevenue_trading = VDSrevenue, cost_trading = cost, rel_cost_trading = rel_cost)

@@

@@

alphas <- c(0, 0.25, 0.5, 0.75, 1)

@@

allocation <-
  expand.grid(
    R = Rvec,
    theta = c(0.25, 0.5, 0.75),
    alpha = alphas,
    trade = T
  ) %>%
  as_tibble() %>%
  mutate(
    resutls = future_pmap(
      .l = list(
        alpha = alpha,
        R = R,
        theta = theta,
        trade = trade
      ),
      .f = allocate_wrap, 
      fvec = fvec,
      r = r,
      K = K,
      p = p,
      q = q,
      Xvec = Xvec,
      beta = beta,
      c = c,
      E = E
    )
  ) %>%
  unnest() %>%
  filter(country == "KIR") %>%
  mutate(
    rev_dir = Ei * pi,
    deltaE = Ea - Ei,
    rev_sells = deltaE * pi,
    rev_tot = rev_dir + rev_sells,
    fct = delta ^ year,
    rev_tot_disc = rev_tot * fct
  )

@@

```{r, fig.height = 3.5, fig.width = 4.5}
(allocation_cost_plot <- allocation %>%
   filter(R > 0,
          trade) %>% 
   mutate(trade = ifelse(trade, "Trading", "No Trading"),
          theta = as.character(theta)) %>% 
   group_by(trade, alpha, R, theta) %>%
   summarize(rev = sum(rev_tot)) %>%
   ungroup() %>%
   mutate(cost = (best_rev - rev) / best_rev) %>%
   ggplot(aes(x = R, y = cost, color = alpha, group = paste(alpha, theta), linetype = theta)) +
   geom_line(size = 1.5) +
   scale_y_continuous(labels = scales::percent,
                      limits = c(0, 1)) +
   xlab("Portion of patch as reserve (R)") +
   ylab("Losses\n(relative to R = 0)") +
   scale_color_viridis_c() +
   scale_linetype_manual(values = c("solid", "dashed", "dotted")) +
   ggtheme_plot() +
   # facet_wrap(~trade, ncol = 1) +
   guides(color = guide_colorbar(title = quo("Allocation\nparameter ("~alpha~")"),
                                 ticks.colour = "black",
                                 frame.colour = "black"),
          linetype = guide_legend(title = quo("Movement\nparameter ("~theta~")"),
                                  override.aes = list(size = 0.5))))
```

```{r}
#Paper export
ggsave(
  plot = allocation_cost_plot,
  filename = here("docs", "img", "allocation_cost_plot.pdf"),
  width = 4.5,
  height = 3.5
)
```

@@

```{r, eval = F}
allocation %>%
  filter(!trade) %>% 
  ggplot(aes(x = year, y = Ea, color = R, group = paste(alpha, R, theta))) +
  geom_line(size = 1) +
  facet_grid(alpha ~ theta) +
  scale_color_viridis_c() +
  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
  ggtheme_plot()
```

```{r, eval = F}
allocation %>%
  filter(theta == 0.5, !trade) %>% 
  ggplot(aes(x = year, y = Xi, color = R, group = paste(alpha, R))) +
  geom_line(size = 1) +
  facet_grid(~alpha) +
  scale_color_viridis_c() +
  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
  ggtheme_plot()
```

>>>>

Create a table

@@

params %>% 
  knitr::kable(col.names = c("Parameter", "Value", "Source"),
               format = "html",
               escape = F) %>% 
  kableExtra::kable_styling(latex_options = "scale_down")
```

Export the table

```{r}
params %>% 
  knitr::kable(col.names = c("Parameter", "Value", "Source"),
               format = "latex",
               escape = F) %>% 
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  cat(file = here("docs", "tab", "parameters.tex"))
```

@@

shorter_trading <- DF_1_with_trading %>% 
  select(Country, R, theta, Vessel_Days_trading = Vessel_Days, pi_trading = VDSprice, VDSrevenue_trading = all_VDSrevenue, cost_trading = cost, rel_cost_trading = rel_cost)

@@

# Change in effort and revenue with and without trading

```{r}
# Create a data.frame of effort by scenario
effort <- both %>% select(R, theta, Vessel_Days, Vessel_Days_trading) %>%
  gather(model, effort, -c(R, theta)) %>%
  mutate(model = ifelse(str_detect(model, "trading"), "Trading", "No trading"))

# Repeat for revenues and merge
revenues <- both %>% select(R, theta, VDSrevenue, VDSrevenue_trading) %>%
  gather(model, revenues, -c(R, theta)) %>%
  mutate(model = ifelse(str_detect(model, "trading"), "Trading", "No trading")) %>%
  left_join(effort, by = c("R", "theta", "model"))
```

Plot it

```{r, fig.width = 6, fig.height = 4}
(
  effort_and_revenues <- ggplot(data = revenues,
                                mapping = aes(x = effort / 1e3,
                                              y = revenues / 1e6,
                                              fill = theta,
                                              size = R,
                                              shape = model)) +
    geom_point(color = "black") +
    scale_fill_viridis_c() +
    scale_shape_manual(values = c(24, 21)) +
    labs(x = "Vessel-days (1,000)", y = "Revenue (million US$)") +
    guides(shape = guide_legend(title = "Scenario"),
           size = guide_legend(title = "Reserve size (R)"),
           fill = guide_colorbar(title = quo("Movement ("~theta~")"),
                                 frame.colour = "black",
                                 ticks.colour = "black"))
)
```

Save it

```{r}
ggsave(plot = effort_and_revenues,
       file = here("docs", "img","effort_and_revenues.pdf"),
       width = 6,
       height = 4)
```

@@

alphas <- c(0, 0.5, 1)

@@

allocation <-
  expand.grid(
    R = Rvec,
    theta = c(0, 0.25, 0.5, 0.75, 1),
    alpha = alphas,
    trade = T
  ) %>%
  as_tibble() %>%
  mutate(
    resutls = future_pmap(
      .l = list(
        alpha = alpha,
        R = R,
        theta = theta,
        trade = trade
      ),
      .f = allocate_wrap, 
      fvec = fvec,
      r = r,
      K = K,
      p = p,
      q = q,
      Xvec = Xvec,
      beta = beta,
      c = c,
      E = E
    )
  ) %>%
  unnest() %>%
  filter(country == "KIR") %>%
  mutate(
    rev_dir = Ei * pi,
    deltaE = Ea - Ei,
    rev_sells = deltaE * pi,
    rev_tot = rev_dir + rev_sells,
    fct = delta ^ year,
    rev_tot_disc = rev_tot * fct
  )

@@

```{r, fig.height = 3.5, fig.width = 5.5}
(allocation_cost_plot <- allocation %>%
   filter(R > 0,
          trade) %>% 
   mutate(trade = ifelse(trade, "Trading", "No Trading"),
          alpha = as.character(alpha)) %>% 
   group_by(trade, alpha, R, theta) %>%
   summarize(rev = sum(rev_tot)) %>%
   ungroup() %>%
   mutate(cost = (best_rev - rev) / best_rev) %>%
   ggplot(aes(x = R, y = cost, color = theta, group = paste(alpha, theta), linetype = alpha)) +
   geom_line(size = 1.5) +
   scale_y_continuous(labels = scales::percent,
                      limits = c(0, 1)) +
   xlab("Portion of patch as reserve (R)") +
   ylab("Losses\n(relative to R = 0)") +
   scale_color_viridis_c() +
   scale_linetype_manual(values = c("solid", "dashed", "dotted")) +
   ggtheme_plot() +
   guides(color = guide_colorbar(title = bquote("Movement ("~theta~")"),
                                 ticks.colour = "black",
                                 frame.colour = "black"),
          linetype = guide_legend(title = bquote("Allocaion ("~alpha~")"),
                                  override.aes = list(size = 0.5))))
```

```{r}
#Paper export
ggsave(
  plot = allocation_cost_plot,
  filename = here("docs", "img", "allocation_cost_plot.pdf"),
  width = 5.5,
  height = 3.5
)
```

@@
